Awareness and Experience of Developers to\\ Outdated and License-Violating Code on Stack Overflow:\\ An Online Survey

### 2018-05-14 cloverflow_technical_report/cloverflow_survey_rn.tex
Removed unwanted subsection (RN).
Added the RN number.
Fixed a wrong stat in the technical repot.

\rnnumber{17/xx}
%\usepackage[table]{xcolor}% http://ctan.org/pkg/xcolor
%\newtheorem{definition}{Definition}

@@

\subsection{Visitor Responses}

@@

Stack Overflow visitors rarely report the problems back to the discussion
threads (as can be seen in
Figure~\ref{fig:survey_visitor_freq_report_problems}). Among the 32 participants
who encounter problems of Stack Overflow snippets, 18 of them (56\%) never
report the problems. Fourteen participants who reported the problems
did so by writing a comment (10), down-voting the answer (8), contacted the
answerer (2), and posting the new and correct answer (2) (shown in
Figure~\ref{fig:survey_visitor_how_report_problems}).

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][2.2cm]{0.98\textwidth}{%
		\textit{For RQ4, our survey results show that 57 out of 87 Stack Overflow
			visitors encountered a problem from reusing Stack Overflow code snippets. Ten
			participants experienced problems for more than 80\% of the copied snippets and
			sixteen participants faced problems for 40--60\% of the reused code. The
			problems ranked by frequency include mismatched solutions (40), outdated
			solutions (39), incorrect solutions (28), and buggy code (1). Fifty-six percent
			of the participants never report the problems back to Stack Overflow.}}%
} \vspace{0.5cm}

@@

\subsubsection{Stack Overflow Visitors}

>>>>

\rnnumber{17/10}
%\usepackage[table]{xcolor}% http://ctan.org/pkg/xcolor
%\newtheorem{definition}{Definition}

@@

\subsection{The visitor survey}

@@

Stack Overflow visitors rarely report the problems back to the discussion
threads (as can be seen in
Figure~\ref{fig:survey_visitor_freq_report_problems}). Among the 57 participants
who encounter problems of Stack Overflow snippets, 36 of them (63.2\%) never
report the problems. Fourteen participants who reported the problems
did so by writing a comment (10), down-voting the answer (8), contacted the
answerer (2), and posting the new and correct answer (2) (shown in
Figure~\ref{fig:survey_visitor_how_report_problems}).

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][2.2cm]{0.98\textwidth}{%
		\textit{For RQ4, our survey results show that 57 out of 87 Stack Overflow
			visitors encountered a problem from reusing Stack Overflow code snippets. Ten
			participants experienced problems for more than 80\% of the copied snippets and
			sixteen participants faced problems for 40--60\% of the reused code. The
			problems ranked by frequency include mismatched solutions (40), outdated
			solutions (39), incorrect solutions (28), and buggy code (1). Sixty-three percent
			of the participants never report the problems back to Stack Overflow.}}%
} \vspace{0.5cm}

@@

%\subsubsection{Stack Overflow Visitors}
